Accessing the nucleon tensor structure in inclusive deep inelastic scattering

### 2016-07-25 1607 - JMC for g2/Paper/JMC_dis.tex
fixed first sentences and naming

Motivated by large-$x$ mass corrections to inclusive DIS structure functions,
Accardi and Qiu have introduced in the LO handbag diagram a ``jet correlator''
that accounts for invariant mass production in the current jet, and ensures
that leading twist calculations in collinear factorization are consistent with
the requirement imposed by baryon number conservation that $x_B<1$
\cite{Accardi-Qiu}. The jet correlator is depicted in
Figure~\ref{fig:handbags}(a) and is defined as 
\begin{align} 
\Xi_{ij}(l,n_+) =\int
  \frac{\de^4\eta}{(2\pi)^4}\; e^{i l \cdot \eta}\,
    \langle 0|\, {\cal U}^{n_+}_{(+\infty,\eta)}
\,\psi_i(\eta)
             \bar{\psi}_j(0)\,
{\cal U}^{n_+}_{(0,+\infty)}\,   |0 \rangle \ ,
\label{e:xifull}
\end{align} 
In this definition, $l$ is the quark four-momentum, $\Psi$ the quark field
operator (with quark flavor index omitted for simplicity), and $|0\rangle$ is
the nonperturbative vacuum state. Furthermore, we explicitly guarantee the
correlator's gauge invariance by introducing two Wilson line operators ${\cal
  U}^{n_+}$ along a light-cone plus direction determined by the vector
$n_+$. This path choice for the Wilson line is required by QCD factorization
theorems, and the vector is determined by the particular hard process to which
the jet correlator contributes. For example, in the case of inclusive DIS
discussed in this paper, this is determined by the four momentum transfer $q$
and the proton's momentum $p$.

The correlator $\Xi$ can be parametrized in terms of scalar functions, using the vectors $l$ and $n_+$: 
\begin{equation}
\Xi(l,n_+) = \Lambda A_1(l^2)\,{\bm 1} + A_2(l^2)\,\lslash 
+ \frac{\Lambda^2}{l \cdot n_{+}} \nslash_+ \, B_{1}(l^2)
+ \frac{i \Lambda}{2 l \cdot n_{+}} [\,\lslash,\nslash_+ ] \, B_{2}(l^2) \ .
\label{e:jetexpansion}
\end{equation} 
Time reversal invariance in QCD requires $B_{2}=0$, while $B_{1}$ contributes
only at twist-4 order, and will not be considered further in this paper. We
focus, instead, on the role of chiral odd terms in the $g_2$ structure function up to twist 3. At this order, 
\begin{equation}
  \Xi(l,n_+) = \Lambda A_1(l^2)\,{\bm 1} + A_2(l^2)\,\lslash 
    + O(\Lambda^2/Q^2)
\label{e:jetexpansion-tw3}
\end{equation} 
is nothing else than the full quark propagator; note however, that we consider
here the full QCD vacuum rather than the perturbative one.  
The $A_1$ and $A_2$ terms can be nicely interpreted in terms of the spectral representation of the cut quark propagator \cite{D'Hoker-lecture-notes,Romao-lecture-notes},
\begin{align} 
  \Xi(l) =  
  \int d \mu^2 \big[ J_1 (\mu^2)\,\mu + J_2 (\mu^2)\,\lslash \big] \,
  \delta(l^2 -\mu_j^2) \ ,
\label{e:jetspectral}
\end{align}
where $\mu^2$ is interpreted as the invariant mass of the current jet, {\it i.e.}, of the particles going through the cut in the top blob of Fig.\ref{fig:handbags}(a), and the $J_i$ are the spectral functions of the quark propagator, that have been also called ``jet functions'' in \cite{Accardi-Qiu,Collins-book?,SCET?}. These satisfy
\begin{align}
  J_2(\mu^2) \geq J_1(\mu^2) \geq 0
  \hspace*{0.5cm} \text{and} \hspace*{0.5cm}
  \int d\mu^2 J_2(\mu^2) = 1 \ .
\label{eq:jetfnsprops}
\end{align}
From a comparison of Eqns.\eqref{e:jetexpansion} and \eqref{e:jetspectral}, one can see that 
\begin{align}
  A_1(l^2)&=\frac{\sqrt{l^2}}{\Lambda}J_1(l^2) & A_2(l^2)&=J_2(l^2) \ .
  \label{eq:jet_vs_spectral}
\end{align}

@@

When inserting the jet correlator in the handbag diagram for inclusive DIS, the invariant jet mass $\mu^2$ is integrated from 0 to $Q^2(1/x_B-1)$. This induces (kinematical) corrections of order $O(1/Q^2)$, whose effect on the $F_2$ structure function has been studied in Ref.~\cite{Accardi-Qiu}:

@@

It is important to notice that $\xi_2=1$ exactly due to CPT invariance \cite{Weinberg-book}, while $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined. From the analytic properties of spectral functions we may expect \cite{Accardi-Qiu)} $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2 (\mu^2) \theta (\mu^2-m_\pi^2)$ with the continuum starting at $m_\pi$, the mass of the pion, due to color confinement effects. Taking into account that $J_1 < J_2$, we may therefore expect 

@@

Extending the analysis of \cite{Accardi-Qiu} to the calculation of twist-3
structure functions requires not only to consider the $\xi_1$ term in the jet
correlator, but also quark-gluon-quark correlators in both the proton and the
vacuum as depicted in Figs.\ref{fig:handbags}(b) and (c), respectively. 
In the former the $\xi_1$ terms contribute to $O(1/Q^2)$, so that up $O(1/Q)$
these give the same contribution as in the conventional handbag calculation.

>>>>

Motivated by large-$x$ mass corrections to inclusive DIS structure functions,
Accardi and Qiu have introduced in the LO handbag diagram 
a ``jet correlator'' (also called ``jet factor'' by Collins and Rogers in Ref.~\cite{Collins:2007ph})
that accounts for invariant mass production in the current jet, and ensures
that leading twist calculations in collinear factorization are consistent with
the requirement imposed by baryon number conservation that $x_B<1$
\cite{Accardi:2008ne}. The jet correlator is depicted in
Figure~\ref{fig:handbags}(a) and is defined as 
\begin{align} 
\Xi_{ij}(l,n_+) =\int
  \frac{\de^4\eta}{(2\pi)^4}\; e^{i l \cdot \eta}\,
    \langle 0|\, {\cal U}^{n_+}_{(+\infty,\eta)}
\,\psi_i(\eta)
             \bar{\psi}_j(0)\,
{\cal U}^{n_+}_{(0,+\infty)}\,   |0 \rangle \ ,
\label{e:xifull}
\end{align} 
In this definition, $l$ is the quark four-momentum, $\Psi$ the quark field
operator (with quark flavor index omitted for simplicity), and $|0\rangle$ is
the nonperturbative vacuum state. Furthermore, we explicitly guarantee the
correlator's gauge invariance by introducing two Wilson line operators ${\cal
  U}^{n_+}$ along a light-cone plus direction determined by the vector
$n_+$. This path choice for the Wilson line is required by QCD factorization
theorems, and the vector is determined by the particular hard process to which
the jet correlator contributes. For example, in the case of inclusive DIS
discussed in this paper, this is determined by the four momentum transfer $q$
and the proton's momentum $p$.

The correlator $\Xi$ can be parametrized in terms of jet parton correlation
functions (PCFs), using the vectors $l$ and $n_+$: 
\begin{equation}
\Xi(l,n_+) = \Lambda A_1(l^2)\,{\bm 1} + A_2(l^2)\,\lslash 
+ \frac{\Lambda^2}{l \cdot n_{+}} \nslash_+ \, B_{1}(l^2)
+ \frac{i \Lambda}{2 l \cdot n_{+}} [\,\lslash,\nslash_+ ] \, B_{2}(l^2) \ .
\label{e:jetexpansion}
\end{equation} 
Time reversal invariance in QCD requires $B_{2}=0$, while $B_{1}$ contributes
only at twist-4 order, and will not be considered further in this paper. We
focus, instead, on the role of chiral odd terms in the $g_2$ structure function up to twist 3. At this order, 
\begin{equation}
  \Xi(l,n_+) = \Lambda A_1(l^2)\,{\bm 1} + A_2(l^2)\,\lslash 
    + O(\Lambda^2/Q^2)
\label{e:jetexpansion-tw3}
\end{equation} 
is nothing else than the full quark propagator; note however, that we consider
here the full QCD vacuum rather than the perturbative one.  
The $A_1$ and $A_2$ terms can be nicely interpreted in terms of the spectral representation of the cut quark propagator \cite{D'Hoker-lecture-notes,Romao-lecture-notes},
\begin{align} 
  \Xi(l) =  
  \int d \mu^2 \big[ J_1 (\mu^2)\,\mu + J_2 (\mu^2)\,\lslash \big] \,
  \delta(l^2 -\mu_j^2) \ ,
\label{e:jetspectral}
\end{align}
where $\mu^2$ is interpreted as the invariant mass of the current jet, {\it
  i.e.}, of the particles going through the cut in the top blob of
Fig.\ref{fig:handbags}(a), and the $J_i$ are the spectral functions of the
quark propagator, that have been also called ``jet functions'' in
\cite{Accardi:2008ne,SCET?} or ``jet factors''~\cite{Collins:2007ph}. These satisfy
\begin{align}
  J_2(\mu^2) \geq J_1(\mu^2) \geq 0
  \hspace*{0.5cm} \text{and} \hspace*{0.5cm}
  \int d\mu^2 J_2(\mu^2) = 1 \ .
\label{eq:jetfnsprops}
\end{align}
From a comparison of Eqns.\eqref{e:jetexpansion} and \eqref{e:jetspectral}, one can see that 
\begin{align}
  A_1(l^2)&=\frac{\sqrt{l^2}}{\Lambda}J_1(l^2) & A_2(l^2)&=J_2(l^2) \ .
  \label{eq:jet_vs_spectral}
\end{align}

@@

When inserting the jet correlator in the handbag diagram for inclusive DIS, the invariant jet mass $\mu^2$ is integrated from 0 to $Q^2(1/x_B-1)$. This induces (kinematical) corrections of order $O(1/Q^2)$, whose effect on the $F_2$ structure function has been studied in Ref.~\cite{Accardi:2008ne}:

@@

It is important to notice that $\xi_2=1$ exactly due to CPT invariance \cite{Weinberg-book}, while $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined. From the analytic properties of spectral functions we may expect \cite{Accardi:2008ne)} $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2 (\mu^2) \theta (\mu^2-m_\pi^2)$ with the continuum starting at $m_\pi$, the mass of the pion, due to color confinement effects. Taking into account that $J_1 < J_2$, we may therefore expect 

@@

Extending the analysis of \cite{Accardi:2008ne} to the calculation of twist-3
structure functions requires not only to consider the $\xi_1$ term in the jet
correlator, but also quark-gluon-quark correlators in both the proton and the
vacuum as depicted in Figs.\ref{fig:handbags}(b) and (c), respectively. 
In the former the $\xi_1$ terms contribute to $O(1/Q^2)$, so that up $O(1/Q)$
these give the same contribution as in the conventional handbag calculation.
